---
title: "Knitr Crossrefs"
author: "Jane Doe"
date: "March 22nd, 2021"
format: 
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning=FALSE)
```

::: {.callout-tip}
## Learn more
See the full guide on [Cross References](https://quarto.org/docs/authoring/cross-references.html).
:::

## Figures

```` {.markdown}
```{r}
#| label: fig-random
#| fig-cap: "Random"
```
````

```{r}
#| label: fig-random
#| fig-cap: "Random"
#| code-fold: true
library(ggplot2)
dat <- data.frame(cond = rep(c("A", "B"), each=10),
                  xvar = 1:20 + rnorm(20,sd=3),
                  yvar = 1:20 + rnorm(20,sd=3))

ggplot(dat, aes(x=xvar, y=yvar)) +
    geom_point(shape=1) + 
    geom_smooth() 
```

See @fig-random.

## Sub-Figures

```` {.markdown}
```{r}
#| label: fig-multiple
#| fig-cap: "Multiple"
#| fig-subcap: ["Pressure", "Cars"]
#| layout-ncol: 2
```
````

```{r}
#| label: fig-multiple
#| fig-cap: "Multiple"
#| fig-subcap: ["Pressure", "Cars"]
#| layout-ncol: 2
plot(pressure)
plot(cars)
```

See @fig-multiple-1 and @fig-multiple-2.

## Tables

```` {.markdown}
```{r}
#| label: tbl-mtcars
#| tbl-cap: "mtcars"
```
````

```` See @tbl-mtcars. ````

```{r}
#| label: tbl-mtcars
#| tbl-cap: "mtcars"
library(knitr)
kable(head(mtcars))
```

See @tbl-mtcars.

## Sub-Tables

```` {.markdown}
```{r}
#| label: tbl-tables
#| tbl-cap: "Tables"
#| tbl-subcap: ["Cars", "Pressure"]
#| layout-ncol: 2
```
````

```` See @tbl-tables-2 ````

```{r}
#| label: tbl-tables
#| tbl-cap: "Tables"
#| tbl-subcap: ["Cars", "Pressure"]
#| layout-ncol: 2
#| echo: false
library(knitr)
kable(head(cars))
kable(head(pressure))
```

See @tbl-tables-2.




