---
title: "HTML Basics"
format: html
comments:
  hypothesis: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning=FALSE)
```

## Overview

Use the `html` format to create HTML output. For example:

```yaml
---
title: "My document"
format:
  html:
    toc: true
    html-math-method: katex
    css: styles
---
```

This example highlights a few of the options available for HTML output. This document covers these and other options in detail.

```{r, child=c("../authoring/_document-options-begin.Rmd")}
```

## CSS Styles

To add a CSS stylesheet to your document, just provide the `css` option. For example:

``` {.yaml}
format:
  html: 
    css: styles.css
```

Using the `css` option works well for simple tweaks to document appearance. If you want to do more extensive customiation see the documentation on [HTML Themes](html-themes.md).

## LaTeX Equations

By default, LaTeX equations are rendered using [MathJax](https://www.mathjax.org/). Use the `html-math-method` option to choose another method. For example:

``` {.yaml}
format:
  html:
    html-math-method: katex
```

You can also specify a `url` for the library to load for a given method:

``` {.yaml}
html-math-method:
  method: mathjax
  url: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
```

Available math rendering methods include:

| Method    | Description                                                                                                                                                                                                                      |
|-----------|----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| `mathjax` | Use [MathJax](https://www.mathjax.org/) to display embedded TeX math in HTML output.                                                                                                                                             |
| `katex`   | Use [KaTeX](https://github.com/Khan/KaTeX) to display embedded TeX math in HTML output.                                                                                                                                          |
| `webtex`  | Convert TeX formulas to `<img>` tags that link to an external script that converts formulas to images.                                                                                                                           |
| `gladtex` | Enclose TeX math in `<eq>` tags in HTML output. The resulting HTML can then be processed by [GladTeX](https://humenda.github.io/GladTeX/) to produce images of the typeset formulas and an HTML file with links to these images. |
| `mathml`  | Convert TeX math to [MathML](https://www.w3.org/Math/) (note that currently only Firefox and Safari natively support MathML)                                                                                                     |
| `plain`   | No special processing (formulas are put inside a `span` with `class="math").`                                                                                                                                                    |

Note that this is more detailed documentation on each of these options in the Pandoc [Math Rendering in HTML](https://pandoc.org/MANUAL.html#math-rendering-in-html) documentation.

## Code Blocks

### Folding

Click the **Code** button to see the code that produced this plot.

```{r}
#| fold: true

library(ggplot2)
dat <- data.frame(cond = rep(c("A", "B"), each=10),
                  xvar = 1:20 + rnorm(20,sd=3),
                  yvar = 1:20 + rnorm(20,sd=3))

ggplot(dat, aes(x=xvar, y=yvar)) +
    geom_point(shape=1) + 
    geom_smooth() 
```

Code folding can be set globally or on a per-chunk basis (chunks can be set to display folded or unfolded by default). For example:

``` {.yaml}
format:
  html:
    code-fold: true
    code-summary: "Show the code"
```

Note that we've also customized summary text that appears in place of the code (the default is just "Code").

Valid values for `code-fold` include:

| `false` | No folding (default)         |
|---------|------------------------------|
| `true`  | Fold code (initially hidden) |
| `show`  | Fold code (initially shown)  |

Use the `fold` and `summary` chunk attributes to control this on a chunk-by-chunk basis:

```` {.python}
```{r}`r ''`
#| fold: true
#| summary: "Show the code"

```
````

### Copy Button

Hover over the code block below and you will see a copy icon in the top-right corner:

```{r eval=FALSE}
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```

This behavior is enabled by default but you configure it using the `code-copy` option:

``` {.yaml}
format:
  html:
    code-copy: false
```

Valid values for `code-copy` include:

+----------------------------------+-----------------------------------+
| `hover`                          | Show button on hover (default)    |
+==================================+===================================+
| `true`                           | Always show code copy button      |
+----------------------------------+-----------------------------------+
| `false`                          | Never show code copy button       |
+----------------------------------+-----------------------------------+

### Linking

The `code-link` option enables hyper-linking of functions within code blocks to their online documentation:

``` {.yaml}
format:
  html:
    code-link: true
```

Code linking is currently implemented only for the knitr engine (via the [downlit](https://downlit.r-lib.org) package).

## Self Contained

HTML documents typically have a number of external dependencies (e.g. images, CSS style sheets, JavaScript, etc.). By default these dependencies are placed in a `_files` directory alongside your document. For example, if you render `report.md` to HTML:

``` {.bash}
$ quarto render report.md --to html
```

Then the following output is produced:

``` {.ini}
report.html
report_files/
```

You might alternatively want to create an entirely self-contained HTML document (with images, css, etc. embedded into the HTML file). You can do this by specifying the `self-contained` option:

``` {.yaml}
format:
  html
    self-contained: true
```

This will produce a standalone HTML file with no external dependencies, using `data:` URIs to incorporate the contents of linked scripts, style sheets, images, and videos. The resulting file should be "self-contained," in the sense that it needs no external files and no net access to be displayed properly by a browser.

## Anchor Sections

Hover over a section title to see an anchor link. Enable/disable this behavior with:

``` {.yaml}
format:
  html:
    anchor-sections: true
```

Anchor links are also automatically added to figures and tables that have a [cross reference](../authoring/cross-references.md) defined.

## Reference Popups

Hover over @xie2015 to see a reference to the definitive book on knitr[^1].

[^1]: knitr is an R package for creating dynamic documents.

Control this behavior with the following options:

``` {.yaml}
format:
  html:
    hover-citations: true
    hover-footnotes: true
```

## Commenting

This page has commenting with [Hypothes.is](https://web.hypothes.is/) enabled via the following YAML option:

``` {.yaml}
comments:
  hypothesis: true
```

You can see the Hypothesis UI at the far right of the page. Rather than `true`, you can specify any of the available Hypothesis [embedding options](https://h.readthedocs.io/projects/client/en/latest/publishers/config/) as a sub-key of `hypothesis`. For example:

``` {.yaml}
comments:
  hypothesis: 
    theme: clean
```

You can enable [Utterances](https://utteranc.es/) commenting using the `utterances` option. Here you need to specify at least the Git repo you want to use for storing comments:

``` {.yaml}
comments:
  utterances:
    repo: quarto-dev/quarto-docs
```

You can also specify the other options [documented here](https://utteranc.es/).

```{r, child=c("../authoring/_document-options-end.Rmd")}
```


## References {.unlisted}
