---
title: "Quarto Presentations with Reveal.js"
format:
  revealjs: 
    menu: true
    controls: true
    slide-number: true
    logo: quarto.png
    css: styles.css
    footer: <https://quarto.org>
    header-includes: |
      <base target="_blank"/>
---

## Hello, There

Reveal.js enables you to create beautiful interactive slide decks using HTML. This presentation will show you examples of what it can do, including:

-   Presenting code and LaTeX equations
-   Including computations in slide output
-   Image, video, and iframe backgrounds
-   Fancy transitions and animations
-   Printing to PDF

::: footer
Learn more: [Quarto Presentations](https://quarto.org/docs/presentations/revealjs/)
:::

## Pretty Code {auto-animate="true"}

-   Over 20 syntax highlighting themes available
-   Default theme optimized for accessibility

``` r
# Define a server for the Shiny app
function(input, output) {
  
  # Fill in the spot we created for a plot
  output$phonePlot <- renderPlot({
    # Render a barplot
  })
}
```

::: footer
Learn more: [Syntax Highlighting](https://quarto.org/docs/output-formats/html-code.html#highlighting)
:::

## Code Animations {auto-animate="true"}

-   Over 20 syntax highlighting themes available
-   Default theme optimized for accessibility

``` r
# Define a server for the Shiny app
function(input, output) {
  
  # Fill in the spot we created for a plot
  output$phonePlot <- renderPlot({
    # Render a barplot
    barplot(WorldPhones[,input$region]*1000, 
            main=input$region,
            ylab="Number of Telephones",
            xlab="Year")
  })
}
```

::: footer
Learn more: [Code Animations](https://quarto.org/docs/presentations/revealjs/advanced.html#code-animations)
:::

## Line Highlighting

-   Highlight specific lines for emphasis
-   Incrementally highlight additional lines

``` {.python code-line-numbers="4-5|7|10"}
import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(subplot_kw={'projection': 'polar'})
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```

::: footer
Learn more: [Line Highlighting](https://quarto.org/docs/presentations/revealjs/#line-highlighting)
:::

## Executable Code

```{r}
#| echo: true
#| fig-width: 10
#| fig-height: 4
library(ggplot2)
ggplot(mtcars, aes(hp, mpg, color = am)) +
  geom_point() +  geom_smooth(formula = y ~ x, method = "loess")
```

::: footer
Learn more: [Running Code](https://quarto.org/docs/computations/running-code.html)
:::

## LaTeX Equations

[MathJax](https://www.mathjax.org/) rendering of equations to HTML

:::: columns

::: {.column width="40%"}

```tex
\begin{gather*}
a_1=b_1+c_1\\
a_2=b_2+c_2-d_2+e_2
\end{gather*}

\begin{align}
a_{11}& =b_{11}&
  a_{12}& =b_{12}\\
a_{21}& =b_{21}&
  a_{22}& =b_{22}+c_{22}
\end{align}
```

:::

::: {.column width="60%"}

```{=tex}
\begin{gather*}
a_1=b_1+c_1\\
a_2=b_2+c_2-d_2+e_2
\end{gather*}
```
```{=tex}
\begin{align}
a_{11}& =b_{11}&
  a_{12}& =b_{12}\\
a_{21}& =b_{21}&
  a_{22}& =b_{22}+c_{22}
\end{align}
```

:::



::::


## Column Layout {.smaller}

Arrange content into columns of varying widths:

::: columns
::: {.column width="35%"}
#### Motor Trend Car Road Tests

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles.
:::

::: {.column width="3%"}
:::

::: {.column width="62%"}
```{r}
knitr::kable(head(mtcars)[,c("mpg",	"cyl", "disp", "hp", "wt")])
```
:::
:::

::: footer
Learn more: [Multiple Columns](https://quarto.org/docs/presentations/revealjs/#multiple-columns)
:::

## Incremental Lists

Lists can optionally be displayed incrementally:

::: incremental
-   First item
-   Second item
-   Third item
:::

. . .

<br/> Insert pauses to make other types of content display incrementally.

::: footer
Learn more: [Incremental Lists](https://quarto.org/docs/presentations/revealjs/#incremental-lists)
:::

## Fragments

Incremental text display and animation with fragments:

<br/>

::: {.fragment .fode-in}
Fade in
:::

::: {.fragment .fade-up}
Slide up while fading in
:::

::: {.fragment .fade-left}
Slide left while fading in
:::

::: {.fragment .fade-in-then-semi-out}
Fade in then semi out
:::

. . .

::: {.fragment .strike}
Strike
:::

::: {.fragment .highlight-red}
Highlight red
:::

::: footer
Learn more: [Fragments](https://quarto.org/docs/presentations/revealjs/advanced.html#fragments)
:::

## Slide Backgrounds {background="#43464B"}

Set the `background` attribute on a slide to change the background color (all CSS color formats are supported).

Different background transitions are available via the `background-transition` option.

::: footer
Learn more: [Slide Backgrounds](https://quarto.org/docs/presentations/revealjs/#color-backgrounds)
:::

## Media Backgrounds {background="#43464B" background-image="images/milky-way.jpeg"}

You can also use the following as a slide background:

-   An image: `background-image`

-   A video: `background-video`

-   An iframe: `background-iframe`

::: footer
Learn more: [Media Backgrounds](https://quarto.org/docs/presentations/revealjs/#image-backgrounds)
:::

## Position Elements Anywhere

![](https://placekitten.com/400/350){.r-absolute top="170" left="30" width="400" height="350"}

![](https://placekitten.com/450/250){.r-absolute .fragment top="90" right="80" width="450" height="250"}

![](https://placekitten.com/300/200){.r-absolute .fragment bottom="80" right="130" width="300" height="200"}

::: footer
Learn more: [Absolute Position](https://quarto.org/docs/presentations/revealjs/advanced.html#absolute-position)
:::

## Slide Transitions {.smaller}

This slide will transition to the next using the `slide` transition

| Transition | Description                                                            |
|------------|------------------------------------------------------------------------|
| `none`     | No transition (default, switch instantly)                              |
| `fade`     | Cross fade                                                             |
| `slide`    | Slide horizontally                                                     |
| `convex`   | Slide at a convex angle                                                |
| `concave`  | Slide at a concave angle                                               |
| `zoom`     | Scale the incoming slide so it grows in from the center of the screen. |

::: footer
Learn more: [Slide Transitions](https://quarto.org/docs/presentations/revealjs/advanced.html#slide-transitions)
:::

## Tabsets {.smaller .scrollable transition="slide"}

::: panel-tabset
### Plot

```{r}
library(ggplot2)
ggplot(mtcars, aes(hp, mpg, color = am)) +
  geom_point() +  geom_smooth(formula = y ~ x, method = "loess")
```

### Data

```{r}
knitr::kable(mtcars)
```
:::

::: footer
Learn more: [Tabsets](https://quarto.org/docs/presentations/revealjs/#tabsets)
:::
