---
title: "Quarto Computations"
format:
  html:
    code-fold: true
    code-tools: true
    code-link: true
---

```{r}
#| label: load-packages
#| echo: false

library(ggplot2)
```

There are `r nrow(mpg)` observations in our data. 

```{r}
#| echo: false

mean_cty <- round(mean(mpg$cty), 2)
mean_hwy <- round(mean(mpg$hwy), 2)
```

The average city mileage of the cars in our data is _r mean_cty_ and the average highway mileage is _r mean_hwy`.

The plots in Figure @fig-mpg show the relationship between city and highway mileage for 38 popular models of cars. In Figure @fig-mpg-1 the points are colored by the number of cylinders while in Figure @fig-mpg-2 the points are colored by engine displacement.

```{r}
#| label: fig-scatterplot
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-alt: "Scatterplot of city vs. highway mileage for cars, where points are colored by the number of cylinders. The plot displays a positive, linear, and strong relationship between city and highway mileage, and mileage increases as the number cylinders decreases."
#| fig-width: 6
#| fig-height: 3.5

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()
```