---
title: "Finer control over table processing"
---

In Quarto v1.3, we added support for parsing HTML tables as native Pandoc elements, so that sophisticated table layouts are available in more formats. In v1.3, this processing could be disabled only by specifying an option in the HTML table itself, using `quarto-disable-processing="true"`.

In v1.4, this behavior can be controlled by document- and project-level metadata, using the `html-table-processing: none` YAML option:

````qmd
---
html-table-processing: none
---

No HTML tables in this document will be processed.

```{r}
library(huxtable)
# your huxtable tables won't be processed by quarto
```

````

In addition, you can disable the processing selectively in parts of the document, by surrounding the elements with a fenced div having the attribute `{html-table-processing="none"}`:

````qmd
---
html-table-processing: none
---

No HTML tables in this document will be processed.

::: {html-table-processing="none"}

```{r}
library(huxtable)
# your huxtable tables won't be processed by quarto because of
# the surrounding div
```

:::

```{r}
library(gt)
# by your gt tables will be processed as in 1.3
```
````
